Deep Reinforcement Learning for Conservation Decisions

### 2021-05-12 manuscript/manuscript.Rmd
comments for remaining sections
Finished first pass at value-learning

See the appendix for how this is derived. 
The intuition behind this approximation is exactly what we want: the agent will increase the probability of repeating the actions for the inputted states proportional to the size of the return. 
In practice, however, the empirical return tends to have high variance, resulting in a very noisy gradient ascent that impedes learning [@CITE].
To avoid this issue, most policy gradient algorithms replace the empirical return with a different return estimator that has lower variance [@CITE GAE].
A sketch of a simple policy gradient algorithm is shown in FIGURE.

@@

The general motivation is that if we know the Q function under the condition that the given policy visits all state-action pairs [@suttonbarto 131; @Qproof], then we can easily find the optimal action at any state by selecting the action with the highest Q-value: $a_t^* = \underset{a_t}{\text{argmax}} \, Q^\pi (s_t, a_t)$.
In the case that the state-action space can be tractably represented in a table, one could employ a  algorithm, like temporal-difference control -- see Sutton Ch. 6 for details -- which approximates the Q value for every state-action pair [@suttonbarto]. 
Yet, for many decision-making problems, the state-action space cannot be tractably represented in a table; one effective alternative for this case is to use a neural network to approximate the Q-function, a method called deep Q-learning. 
The general process for deep Q-learning differs from policy gradient methods, since instead of trying to maximize the return directly, the objective is to minimize the Bellman error.
The Bellman error

>>>>

See the appendix for how this is derived. 
The intuition behind this approximation is exactly what we want: the agent will increase the probability of repeating the actions for the inputted states proportional to the size of the return. 
In practice, however, the empirical return tends to have high variance, resulting in very noisy gradients that impedes learning [@CITE].
To avoid this issue, most policy gradient algorithms replace the empirical return with a different return estimator that has lower variance [@CITE GAE].
A sketch of a simple policy gradient algorithm is shown in FIGURE.

@@

The general motivation is that if we know the Q function under certain conditions -- e.g. that the state-action space is discrete and that the given policy visits all state-action pairs repeatedly [@suttonbarto 131; @Qproof] --, then we can easily find the optimal action at any state by selecting the action with the highest Q-value: $a_t^* = \underset{a_t}{\text{argmax}} \, Q^\pi (s_t, a_t)$.
In the case that the state-action space can be tractably represented in a table, one could employ a  algorithm, like temporal-difference control -- see Sutton Ch. 6 for details -- which approximates the Q value for every state-action pair [@suttonbarto]. 
Yet, for many decision-making problems, the state-action space cannot be tractably represented in a table; one effective alternative for this case is to use a neural network to approximate the Q-function, a method called deep Q-learning. 
The general process for deep Q-learning differs from policy gradient methods, since instead of trying to maximize the return directly, the objective is to minimize the Bellman error.
The Bellman error is a measure of how distant a given value function is from that value function which has been re-evaluated with recent environment interaction.
In the case where the Q-function is approximated by some neural network and thus represented as $Q_\theta$, the Bellman error for one state-action pair would be

$$
  \mathcal{E} = r(s_t, a_t) + \gamma \, \underset{a}{\text{max}} \, Q_\theta(s_{t+1}, a) - Q_\theta(s_t, a_t).
$$

See the appendix/reference for details on how the Bellman Error is derived from eq. [@CITE]. 
The general scheme for approximate value-learning with deep neural networks is to sample trajectories from the environment, evaluate the Bellman Error across a range of these samples then perform the following gradient descent,

$$
  \theta_{t+1} = \theta_t - \alpha \nabla_\theta \, \sum_i \mathcal{E}_i^2,
$$

where $i$ indexes the sample.
After convergence to the Q function, the optimal policy could
